### 2024-03-04 sections/0intro.tex
Standardized main result citing in introduction.
minor changes until §1.2

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition}
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifolds) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen-equivalences in appropriate ways. The interested reader can find accounts of these matters in e.g. ..... In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.

\end{document}

>>>>

\textbf{\Cref{ch:fact_alg} Factorization Algebras:} The third section introduces the concept of factorization algebras, together with its different variations, like prefactorization algebras and locally constant factorization algebras. Of these, the locally constant factorization algebras will be the ones that capture the different possible stratified structures that a manifold can have, and they will be a large focus of this work. The definitions of these will not be novel. They can be found in the works \cite{cg2016}, \cite{ginot2015} and even \cite{af_primer}. In fact, in the slightly different context of vertex algebras the idea can be traced back to \cite{bd2004}. However, all of the above works take a slightly different perspective in their presentation of the definitions, which we hope to unite in this work. The key result of this section is the following:
%
\begin{theorem*}[\ref{thm:disk_alg=lcfa}]
    There is an equivalence of $\infty$-categories between locally constant factorization algebras over a stratified manifold $M$ and $\disk_{/M}$-algebras
    %
    \begin{equation}
        \int: \alg{\disk_{/M}} (\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_M (\catC),
    \end{equation}
    %
    given by factorization homology,
\end{theorem*}
%
as well as its \cref{cor:disk_alg=falg} for the case of ordinary factorization algebras. These show that the $\infty$-operad governing factorization algebras can be taken to be the slice $\infty$-operad $\disk_{/M}$ (or $\disk[r]_{/M}$ for the ordinary case). We then introduce some operations that we can do with factorization algebras like the pushforward and restriction, as well as state a result for locally constant factorization algebras on product spaces, which confirms a conjecture of \cite{ginot2015}:
%
\begin{proposition*}[\ref{prop:exp_of_products_lc}]
    Let $M$ and $N$ be stratified manifolds. There is an equivalence of $\infty$-categories
    %
    \begin{equation}
        \bar{\pi}: \lcfa_{M \times N}(\catC) \xrightarrow{\ \ \simeq \ \ } \lcfa_{M}(\lcfa_{N}(\catC)).
    \end{equation}
\end{proposition*}
%
Finally, we will examine some examples of factorization algebras whose construction is known, specifically, locally constant factorization algebras on the intervals $(-1,1)$, $[-1,1)$ and $[-1,1]$ as well as Euclidean spaces $\mathbb{R}^n$ more generally.

@@

\textbf{\Cref{ch:classif_defect_mfld} Classifying $\lcfa$s on Defect Manifolds:} The fifth section focuses on the stratified structure and gives a way to express what effect this has on the locally constant factorization algebras. Specifically, we look at the data of a smooth manifold $M$ with a distinguished, properly embedded submanifold $\Sigma$ (also known as a defect submanifold) as the data of a stratified manifold $M_\Sigma$. We will show that, along with giving algebras associated to the different pieces, locally constant factorization algebras on these manifolds, in some (precise) sense, also encode a module structure associated with $\Sigma$.

@@

It is also important to note that we will not be making a notational distinction between topological categories, Kan enriched categories and $\infty$-categories because of the functors
%
\begin{equation}
    \{ \mathsf{Top}\mathrm{-categories}\} \xrightarrow{\mathsf{Sing}} \{ \mathsf{Kan}\mathrm{-categories}\} \xrightarrow{\mathsf{N}} \cat,
\end{equation}
%
which are both Quillen-equivalences in appropriate ways (\cite{joyal2007quasi,bergner2010survey}). In particular, we will not distinguish notationally the nerve of an ordinary category from the ordinary category itself. Similarly, we will not distinguish between (topological) multicategories and their $\infty$-operadic nerve.
\end{document}

### 2024-03-04 sections/1stratified.tex
minor changes until §1.2

\begin{definition}
    Let $P$ be a poset. A \emph{$P$-stratified space} is a topological space $X$ together with a map $X \rightarrow P$, which we call the stratification of $X$. We will sometimes refer to $X$ as the underlying topological space of a stratified space. Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$th stratum of $X$\footnote{Sometimes the name stratum is reserved for the connected components of $X_p$ if strata are required to be connected.}.
\end{definition}

\begin{example}
    Any CW complex $X$ can be made into a stratified space $X \rightarrow \mathbb{N}$, which sends all points in $X_{\leq k} \setminus {X_{\leq k-1}}$ to $k$, where $X_{\leq k}$ is the $k$-skeleton of $X$.
\end{example}

@@

@@

\begin{definition}
    Let $X \rightarrow P$ and $X' \rightarrow P'$ be two stratified spaces. A \emph{continuous stratified map} (or \emph{map of stratified spaces}) is a commutative diagram in $\mathsf{Top}$
    %
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r] \arrow[d] & X' \arrow[d] \\
            P \arrow[r] & P'.
        \end{tikzcd}
    \end{equation}
\end{definition}

@@

Next, we construct the cone of a stratified space. This plays a very important role in the theory of conically smooth manifolds, because it provides the prototypical departure from smoothness. In other words, the local structure of these will always look like a cone over some space with a possible further thickening by some $\mathbb{R}^k$, just as the local structure of smooth manifolds is given by $\mathbb{R}^k$; the cones will be the model spaces for singularities.

\begin{definition}
    Let $X \rightarrow P$ be a stratified space. The cone $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows. At the level of topological spaces we define the pushout in $\mathsf{Top}$
    %
    \begin{equation}
        \mathsf{C}(X) := * \coprod_{X \times \{0\}} X \times \hoint.
    \end{equation}
    %
    At the level of posets we define the pushout in $\mathsf{Poset}$
    %
    \begin{equation}
        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1] \cong P^{\vartriangleleft}.
    \end{equation}
    %
    The standard stratification of $\hoint$ together with the obvious map $* \rightarrow *$ induce a stratification $\mathsf{C}(X) \rightarrow \mathsf{C}(P)$ as a map between pushouts. 
\end{definition}

The equivalent of a topological manifold in the stratified setting is a \emph{$C^0$ stratified space}. We will not be fully precise in the definition of these, since this would stray us from our main goal. We will however cite theorems that show that the spaces we consider in this work are $C^0$ stratified spaces. The reason why the below cannot be the actual definition is because it would partially be a cyclic statement. We cite it because it provides good intuition for the structure of $C^0$ stratified spaces.

@@

\begin{theorem}[{\cite[lem.2.2.2]{aft_localstrut}}]\label{thm:basics_give_basis}
    Let $X$ be a stratified, second countable, Hausdorff space, and consider the collection of open embeddings
    %
    \begin{equation}
        \{ U \xhookrightarrow{} X\},
    \end{equation}
    %
    where $U$ ranges over the $C^0$ basics. Then this collection forms a basis for the topology of $X$ if and only if $X$ is a $C^0$ stratified space.
\end{theorem}

\begin{theorem}[{\cite[cor.2.3.5]{aft_localstrut}}]
    Let $X \rightarrow P$ be a $C^0$ stratified space. For any $p \in P$, the stratified spaces $X_{\leq p}$, $X_{p}$ and $X_{\nless p}$, defined as the relevant preimages, are $C^0$ stratified spaces. Furthermore, $X_p$ is even a topological manifold.
\end{theorem}

For topological spaces we have the concept of covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$. $C^0$ stratified spaces have an additional, related concept called depth. It plays a key role in describing these spaces, especially on the technical side\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular. One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$}. As the name suggests, it conveys information about how deep the stratification is.

@@

A stratified manifold is a $C^0$ stratified space $M$ equipped with an atlas
%
\begin{equation}
    \{\mathbb{R}^{k_\alpha} \times \mathsf{C}(Z_\alpha) \hookrightarrow M\}_\alpha,
\end{equation}
%
whose elements we call basics. This atlas has to be a basis for the topology of $X$, and the transitions maps, open embeddings among basics, have to be conically smooth. General maps of stratified manifolds will then be conically smooth if their representatives in basics are conically smooth.

The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction on depth to define conical smoothness.

In lieu of a definition we give the following illuminating example:
%
\begin{example}[{\cite[ex.1.2]{aft_fhstrat}}]
    Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum. A smooth map $f: Z \xrightarrow{} Z'$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{C}(f)$ between the cones of these manifolds. If we also have a smooth map between Euclidean spaces $g: \mathbb{R}^{n} \xrightarrow{} \mathbb{R}^{n'}$ then the map $g \times \mathsf{C}(f): \mathbb{R}^{n} \times \mathsf{C} (Z) \xrightarrow{} \mathbb{R}^{n'} \times \mathsf{C} (Z')$ is conically smooth. This already allows us to describe stratified manifolds of depth 1.
\end{example}

@@

\begin{definition}
    Let $f: M \rightarrow N$ be a conically smooth map.
    %
    \begin{enumerate}
        \item $f$ is an \emph{open embedding} if it is an open map that is conically diffeomorphic onto its image.
        \item $f$ is a \emph{refinement} if it's a homeomorphism of underlying topological spaces, and its restriction to each stratum of $M$ is an embedding.
        \item Let $P_N$ be the stratifying poset of $N$. $f$ is a \emph{constructible bundle} if, for each $p \in P_N$, the restriction $f|_p: M|_{f^{-1} N_p} \rightarrow N_p$ is a fiber bundle of stratified spaces.
    \end{enumerate}
\end{definition}

\begin{remark}
    We will also on occasion use the concept of \emph{weakly constructible bundle}, which is a continuous stratified map $f: M \rightarrow N$ which is a constructible bundle out of a refinement of $M$, i.e. there is a diagram $M \xleftarrow{r} M' \xrightarrow{s} N$, where there is an equality $f = s \circ r$ of the underlying continuous maps. Constructible bundles are obviously also weakly constructible.
\end{remark}

@@

For the next definition we notice that all standard simplices are stratified manifolds.

\begin{definition}
    $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them. To get the higher categorical structure we consider a simplicial enrichment over $\mathsf{Set}$-valued presheaves on the unenriched category, so that given two objects $M$ and $N$
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Map}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p),
    \end{equation}
    %
    where $\Delta^p$ is the standard $p$-simplex and $\mathsf{Map}_{/\Delta^p}$ denotes those stratified maps that commute with projecting to $\Delta^p$. It can be shown that this enrichment factors through a $\mathsf{Kan}$-enrichment, which gives the appropriate structure.
\end{definition}

>>>>

\begin{definition}
    Let $P$ be a poset. A \emph{$P$-stratified space} is a topological space $X$ together with a continuous map $X \rightarrow P$, which we call the \emph{stratification} of $X$. The poset $P$ is called the \emph{stratifying poset}. We will sometimes refer to $X$ as the underlying topological space of a stratified space. Furthermore, we denote the preimage of $p \in P$ as $X_p$ and call it the $p$'th stratum of $X$\footnote{Sometimes the name stratum is reserved for the connected components of $X_p$ if strata are required to be connected.}.
\end{definition}

\begin{example}\label{54HC9DC}
    Any CW complex $X$ can be made into a stratified space $X \rightarrow \mathbb{N}$, which sends all points in $X_{\leq k} \setminus {X_{\leq k-1}}$ to $k$, where $X_{\leq k}$ is the $k$-skeleton of $X$.
\end{example}

@@

\begin{example}
    Any topological space $X$ can be stratified by its connected components, with $P$ discrete and $|P|=\pi_0(X)$.
\end{example}

@@

\begin{definition}
    Let $X \rightarrow P$ and $X' \rightarrow P'$ be two stratified spaces. A \emph{continuous stratified map} (or \emph{map of stratified spaces}) is a commutative diagram in $\mathsf{Top}$ of type
    %
    \begin{equation}
        \begin{tikzcd}
            X \arrow[r] \arrow[d] & X' \arrow[d] \\
            P \arrow[r] & P'.
        \end{tikzcd}
    \end{equation}
\end{definition}

@@

Next, we construct the cone of a stratified space. This plays a very important role in the theory of conically smooth manifolds, because it provides the prototypical departure from smoothness. In other words, the local structure of these will always look like a cone over some space with a possible further thickening by a factor $\mathbb{R}^k$, just as the local structure of smooth manifolds is given by $\mathbb{R}^k$. The cones will be the model spaces for singularities.

\begin{definition}
    Let $X \rightarrow P$ be a stratified space. Its (\emph{open}) \emph{cone} $\mathsf{C}(X \rightarrow P)$ is the stratified space constructed as follows. At the level of topological spaces we define the pushout in $\mathsf{Top}$
    %
    \begin{equation}
        \mathsf{C}(X) := * \coprod_{X \times \{0\}} X \times \hoint.
    \end{equation}
    %
    At the level of posets we define the pushout in $\mathsf{Poset}$
    %
    \begin{equation}
        \mathsf{C}(P) := * \coprod_{P \times \{ 0\}} P \times [1] \cong P^{\vartriangleleft}.
    \end{equation}
    %
    The standard stratification of $\hoint$ together with the obvious map $* \rightarrow *$ induce a stratification $\mathsf{C}(X) \rightarrow \mathsf{C}(P)$ as a map between pushouts. 
\end{definition}

The following will be used in the definition of the $\infty$-category $\mfld$ of stratified manifolds.

\begin{definition}
    Let $X\to P$ be a stratified space. Its \emph{closed cone} is the stratified space $\overline{C}(X)\to P^{\vartriangleleft}$ with $\overline{C}(X)=\ast\amalg_{X\times\{0\}}X\times[0,1]$ and the obvious stratification.
\end{definition}

The equivalent of a topological manifold in the stratified setting is a \emph{$C^0$ stratified space}. We will not be fully precise in the definition of these, since this would stray us from our main goal. We will however cite theorems that show that the spaces we consider in this work are $C^0$ stratified spaces. The following definition is partly cyclic, but we cite it because it provides good intuition for the structure of $C^0$ stratified spaces.

@@

\begin{theorem}[{\cite[Lemma 2.2.2]{aft_localstrut}}]\label{thm:basics_give_basis}
    Let $X$ be a stratified, second countable, Hausdorff space, and consider the collection of open embeddings
    %
    \begin{equation}
        \{ U \xhookrightarrow{} X\},
    \end{equation}
    %
    where $U$ ranges over the $C^0$ basics. Then this collection forms a basis for the topology of $X$ if and only if $X$ is a $C^0$ stratified space.
\end{theorem}

\begin{theorem}[{\cite[Corollary 2.3.5]{aft_localstrut}}]
    Let $X \rightarrow P$ be a $C^0$ stratified space. For any $p \in P$, the stratified spaces $X_{\leq p}$, $X_{p}$ and $X_{\nless p}$, defined as the relevant preimages, are $C^0$ stratified spaces. Furthermore, $X_p$ is even a topological manifold.
\end{theorem}

For topological spaces we have the concept of (\v{C}ech--Lebesgue) covering dimension $\mathsf{dim}_x (X)$ at a point $x \in X$. $C^0$ stratified spaces have an additional, related concept called depth. It plays a key role in describing these spaces.\footnote{For example, we said that \cref{thm:basics_give_basis}, as a definition, would be circular. One way to resolve this is by induction on depth since $\mathsf{dpt} (\mathbb{R}^n \times \mathsf{C}(Z)) = \mathsf{dpt} (\mathsf{C}(Z)) = \mathsf{dpt} (Z) + 1$} As the name suggests, it conveys information about how deep the stratification is. For instance, if the stratification is given by a filtration as in \Cref{54HC9DC}, then it coincides with the length of the filtration, or equivalently, with the length of the longest non-trivial chain of arrives in the stratifying poset. Similarly to $\mathsf{dim}$ it has a pointwise and a global version.

@@

A stratified manifold is a $C^0$ stratified space $M$ equipped with an atlas
%
\begin{equation}
    \{\mathbb{R}^{k_\alpha} \times \mathsf{C}(Z_\alpha) \hookrightarrow M\}_\alpha,
\end{equation}
%
whose elements we call basics. This atlas has to be a basis for the topology of $X$, and the transitions maps, open embeddings among basics, have to be conically smooth. General maps of stratified manifolds will then be conically smooth if their representatives in basics are conically smooth.
The reason why the definition is involved is, because unlike in the smooth case the presence of the compact spaces $Z_\alpha$ means that we have to use induction on depth to define conical smoothness.

In lieu of a definition we give the following illuminating example:
%
\begin{example}[{\cite[Example 1.2]{aft_fhstrat}}]
    Smooth manifolds fall under the definition of stratified manifolds as those that only have one stratum. A smooth map $f: Z \xrightarrow{} Z'$ between compact smooth manifolds gives rise to a conically smooth map $\mathsf{C}(f)$ between the cones of these manifolds. If we also have a smooth map between Euclidean spaces $g: \mathbb{R}^{n} \xrightarrow{} \mathbb{R}^{n'}$ then the map $g \times \mathsf{C}(f): \mathbb{R}^{n} \times \mathsf{C} (Z) \xrightarrow{} \mathbb{R}^{n'} \times \mathsf{C} (Z')$ is conically smooth. This already allows us to describe stratified manifolds of depth 1.
\end{example}

@@

\begin{definition}
    Let $f: M \rightarrow N$ be a conically smooth map.
    %
    \begin{enumerate}
        \item $f$ is an \emph{open embedding} if it is an open map that is conically diffeomorphic onto its image.
        \item $f$ is a \emph{refinement} if it's a homeomorphism of underlying topological spaces, and its restriction to each stratum of $M$ is an embedding.
        \item Let $P_N$ be the stratifying poset of $N$. Then $f$ is a \emph{constructible bundle} if, for each $p \in P_N$, the restriction $f|_p: M|_{f^{-1} N_p} \rightarrow N_p$ is a fiber bundle of stratified spaces. The map $f$ is a \emph{fiber bundle} if there exists a cover $\{U\hookrightarrow N\}$ of $N$ consisting of open embeddings such that the restriction of $f$ along $U$ is of type $\mathsf{pr}\colon F_U\times U\to U$ for a stratified manifold $F_U$.
    \end{enumerate}
\end{definition}

\begin{remark}
    We will also on occasion use the concept of \emph{weakly constructible bundle}, which is a continuous stratified map $f: M \rightarrow N$ which is a constructible bundle out of a refinement of $M$, i.e. there is a diagram $M \xleftarrow{r} M' \xrightarrow{s} N$, where there is an equality $f = s \circ r$ of the underlying continuous maps. Constructible bundles are obviously also weakly constructible. Their use owes to the Pushforward Theorem \cite[Theorem 2.25]{aft_fhstrat}, which states in particular that algebras may be pushed forward along weakly constructible bundles. 
\end{remark}

@@

For the next definition we notice that all standard simplices are stratified manifolds, obtained as $\Delta^n\cong\overline{C}^n(\ast)\to\overline{C}(\{0\})\cong[n]$.

\begin{definition}
    $\mfld$ is the $\infty$-category whose objects are stratified manifolds and whose morphisms are open embeddings among them. It is presented as the $\mathsf{Kan}$-enriched category of stratified manifolds by taking the Kan complex of morphisms between two objects $M$ and $N$ to be defined by
    %
    \begin{equation}
        \mathsf{Hom}_{\mfld} (M, N): [p] \mapsto \mathsf{Mfld}_{/\Delta^p} (M \times \Delta^p, N \times \Delta^p).
    \end{equation}
    %
    Here, $\mathsf{Mfld}_{/\Delta^p}$ takes the morphism set in the over-category over $\Delta^p$.
\end{definition}

### 2024-03-04 sections/2homology.tex
minor changes until §1.2

Factorization homology (also topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds. We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.

>>>>

Factorization homology (also known as topological chiral homology) is a construction that to the data of a smooth manifold $M$ and an algebra $A$ valued in a symmetric monoidal $\infty$-category $\catC$ assigns an object
%
\begin{equation}
    \int_{M} A \in \catC.
\end{equation}
%
In fact this is only the simplest variant of factorization homology. Variants that accommodate stratified manifolds instead of smooth ones and even $(\infty,n)$-categories instead of algebras have also been worked out. Given the focus of the present work, we will be concerned with the variant that can evaluate stratified manifolds. We will not be interested, however, in generalizing the algebraic input beyond disk algebras to the realm of $(\infty,n)$-categories. Fixing the algebra, the construction is functorial with respect to open embeddings in the manifold variable, which is the starting point to show that it is a chain level homology theory in a generalized sense, and giving the name. The initial chiral version was first introduced in \cite{bd2004}, and a topological version was introduced by \cite{lurie_ha}. Later, in \cref{thm:disk_alg=lcfa}, we will also see how factorization homology serves to construct factorization algebras. The theory of factorization homology has been deeply developed in \cite{af_fhtop, aft_fhstrat}, especially in the manner that we introduce it in here. A good introduction, is thus, given by \cite{af_primer}, which we will be following.
